Adopting agile in the large: motivations, success factors and challenges

### 2014-05-05 journal/article.tex
Customizing badly

>>>>

The difficulty of agile and misunderstandings were also evident in cases where
the methods were customized badly. As by-the-book implementation often was not
feasible the agile method was tailored to suite the needs of the organization.
However, in some cases tailoring meant skipping some practices, which lead into
problems. In one case certain individuals were allowed to ignore some core
elements of Scrum, which came to turn the teams decision making into a variant
of command and control [P9].
Lewis and Neher [P29] describe how there was temptation to strip some practices
and enhance others. Previous attempts had proven that one of the reasons early
attempts of agile had failed was deviations from the process, because of which
the agile mindset did not take root [P29]. In a bad implementation customization
may lead to the team taking only practices that reflect their current needs, and
therefore failing to achieve a real change in process and mindset [P9, P46].
